Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model

### 2014-01-21 Paper/gammaRays.tex
Cleared main.cpp

Gamma Ray Bursts (GRBs) are among the most energetic events in the Universe, therefore they might provide new knowledge for particle physics. Recent observatories, specifically Fermi \cite{Ackermann:2012kna} and Swift \cite{Gehrels:2004gu} allowed for extensive study of these explosions \cite{Vianello:2013ela,Gehrels:2013xd}. These and previous studies led to several interesting results. For example, the total energy emitted in gamma-rays during a burst was found to be similar among different bursts within an order of magnitude \cite{Bloom:2003wy}. This suggests that most of the bursts must have similar energetics in their rest frame. Temporal variations of spectra were also studied. The spectral lags were found between different low energy bands \cite{Yi:2005ht}. The very high energy radiation was discovered to be extended if compared to x-ray emission \cite{Vianello:2013ela,Lange:2013uh}. Moreover, the Large Area Telescope (LAT) of Fermi allows us to explore the spectral variations even between high energy bands like $(\unit[100]{MeV}, \unit[1]{GeV})$ and $(\unit[1]{GeV}, \unit[300]{GeV})$ (we'll call them low and high energy bands). In this paper we use the Kolmogorov-Smirnov test to compute the time stretching of radiation in one of these bands compared to the other.

@@

\subsection{Download and Process}
\subsection{Linear Component (background)}
\subsection{KS-test}
\subsection{Results}

>>>>

Gamma Ray Bursts (GRBs) are among the most energetic events in the Universe, therefore they might provide new knowledge for particle physics. Modern observatories, specifically Fermi \cite{Ackermann:2012kna} and Swift \cite{Gehrels:2004gu} made possible to study these explosions extensively \cite{Vianello:2013ela,Gehrels:2013xd}. These and previous studies led to several interesting results. For example, the total energy emitted in gamma-rays during a burst was found to be similar among different bursts within an order of magnitude \cite{Bloom:2003wy}. This suggests that most of the bursts must have similar energetics in their rest frame. Temporal variations of spectra were also studied. The spectral lags were found between different low energy bands \cite{Yi:2005ht}. The very high energy radiation was discovered to be extended if compared to x-ray emission \cite{Vianello:2013ela,Lange:2013uh}. Moreover, the Large Area Telescope (LAT) of Fermi allows us to explore the spectral variations even between high energy bands like $(\unit[100]{MeV}, \unit[1]{GeV})$ and $(\unit[1]{GeV}, \unit[300]{GeV})$ (we'll call them low and high energy bands). In this paper we use the Kolmogorov-Smirnov test to compute the time stretching of radiation in one of these bands compared to the other.

@@

\subsection{Download and Process}

Download in progress.

\subsection{Linear Component (background)}
\subsection{KS-test}
\subsection{Results}
